Psychophysics of musical elements in the discrete-time representation of sound

### 2014-12-22 article/article.tex
revisada bibliografia do artigo

@@

The Nyquist theorem~\cite{} states that the sampling frequency is twice the maximum frequency of the represented signal. Thus, for general musical purposes, it is necessary to have samples in a rate at least twice the highest frequency heard by humans, that is, $f_s \geq 2\times 20kHz = 40kHz$. This is the fundamental reason for the adoption of sampling frequencies like $44.1kHz$ and $48kHz$, standards in Compact Disks (CD) and broadcast systems (radio and television), respectively.

@@

The remaining parts of this work are organized as follows: section~\ref{sec:discNote} characterizes the basic musical note; section~\ref{sec:internalVar} further develops internals of the musical note; section~\ref{sec:notesMusic} tackles the organization of musical notes in higher levels of musical structure~\cite{Wisnick,Webern,Lerdhal,Cook,Lacerda}. As these descriptions embody topics such as psycho-acoustics, cultural traditions, formalisms and protocols, the text points to external complements as needed~\cite{Zamacois,Schoenberg,microsound}.

@@

The philosophical understanding that human thought is founded on the concept of
similarities and differences (e.g. perceived in stimuli and objects), places symmetries
at the core of cognitive processes~\cite{Deleuze}. Mathematically, symmetries
are algebraic groups, and a finite group is always isomorphic to a permutation
group (by Cayley's theorem). 
In a way, this states that permutations represent any symmetry in a
finite system~\cite{grupos,gruposFascination}.
In music, permutations are ubiquitous and present in scholastic techniques,
 which confirms their central role. 
The successive application of permutations generates cyclic arcs~\cite{change,Zamacois,permMusic}. 
Two academic studies were dedicated to generating musical structures~\cite{figgusOriginal, figgusEspacializacao}.

>>>>

\author{Antônio Pessoti}
  \homepage{}
  \email{debcris.cor@gmail.com}
 \altaffiliation[Instituto de Ci\^encias Matem\'aticas e de Computa\c{c}\~ao ]{ICMC-USP}

@@

The Nyquist theorem~\cite{Openheim} states that the sampling frequency is twice the maximum frequency of the represented signal. Thus, for general musical purposes, it is necessary to have samples in a rate at least twice the highest frequency heard by humans, that is, $f_s \geq 2\times 20kHz = 40kHz$. This is the fundamental reason for the adoption of sampling frequencies like $44.1kHz$ and $48kHz$, standards in Compact Disks (CD) and broadcast systems (radio and television), respectively.

@@

The remaining parts of this work are organized as follows: section~\ref{sec:discNote} characterizes the basic musical note; section~\ref{sec:internalVar} further develops internals of the musical note; section~\ref{sec:notesMusic} tackles the organization of musical notes in higher levels of musical structure~\cite{Wisnick,Webern,Lerdahl,Cook,Lacerda}. As these descriptions embody topics such as psycho-acoustics, cultural traditions, formalisms and protocols, the text points to external complements as needed~\cite{Zamacois,Schoenberg,microsound}.

@@

The philosophical understanding that human thought is founded on the concept of
similarities and differences (e.g. perceived in stimuli and objects), places symmetries
at the core of cognitive processes~\cite{Deleuze}. Mathematically, symmetries
are algebraic groups, and a finite group is always isomorphic to a permutation
group (by Cayley's theorem). 
In a way, this states that permutations represent any symmetry in a
finite system~\cite{gruposFascination}.
In music, permutations are ubiquitous and present in scholastic techniques,
 which confirms their central role. 
The successive application of permutations generates cyclic arcs~\cite{change,Zamacois,permMusic}. 
Two academic studies were dedicated to generating musical structures~\cite{figgusOriginal, figgusEspacializacao}.
